Detecci\'on de malas hierbas a trav\'es\\ de t\'ecnicas de redes neuronales convolucionales y visi\'on artificial

### 2017-05-11 PaperBCJ.tex
Pequeñas Correciones

\section{State of Art}
During the last centuries, huge progress has taken place in science and technology developments. Significant milestones such as Communications, Numerical Computer Control and the miniaturization of components have benefited social and industrial sectors on its approach to solve specific problems. 
\\

Globalization has permitted countries who are not leader technology developers, like Ecuador, to receive leading edge technological products in order to satisfy requirements and propose   solutions to still-unresolved problems.
\\

@@

One of the first approximations to the algorithms of detection of Crops is the developed \cite{Brivot:Marchant}, this could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops. In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently \cite{Cheng:Mason} had been developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN(Density-based spartial clustering of apllications with noise) as Machine Learning, it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice.  \cite{Hong:Lei} Other approximations are the use an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%, \cite{Araguez}  perform their analysis through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document. \cite{Su:Hnin} used the binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed. \cite{Romeo} propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop. \cite{Potena:Nardi} use a multispectral camera to obtain RGB and NIR images, for the segmentation and classification they use a light CNN for the first process and a Deep CNN for classification, its accuracy is up to 98\%. There is an approximation to \cite{Cicco:Potena} CNN through the generation of datasets
\\

@@

  \bibitem{Hong:Lei}
R.~Cheng and J.~A. Mason, \emph{Segmentation of plants and weeds for a precision crop protection robot using infrared images} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 1996.

@@

\bibliography{•}

>>>>

\section{Introduction}
During the last centuries, huge progress has taken place in science and technology developments. Significant milestones such as Communications, Numerical Computer Control and the miniaturization of components have benefited social and industrial sectors on its approach to solve specific problems. 
\\

Globalization has permitted countries who are not leader technology developers, like Ecuador, to receive bleeding edge technological products in order to satisfy requirements and propose solutions to still-unresolved problems.
\\

@@

One of the first approximations to the algorithms of detection of Crops was  developed in 1996\cite{Brivot:Marchant}, this algorithm permitted to segment crops from weed, it could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops. In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently \cite{Cheng:Mason} there had been developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN (Density-based spartial clustering of apllications with noise) , it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice, Araguez \textit{et. al} \cite{Araguez}  performed their segmentation through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document. 
\\

Hong and Lei \cite{Hong:Lei} developed their approximation by using an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%,  also there had been developed \cite{Su:Hnin} methos trough binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed. Romeo \textit{et. al} \cite{Romeo} propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop. The segmentation of weed and crops is not closed in Color Images, using a multispectral camera  \cite{Potena:Nardi} permitted to obtain RGB and NIR images, for the segmentation and classification, then the images used a light CNN for the first process and a Deep CNN for classification in Crops, its accuracy is up to 98\% in the identification of weeds. One of the most dificults things for the identification of crops is the generation of Datasets due to presence of Weed in the images of training, but there could be correctly generated by a Convolutional Neural Network \cite{Cicco:Potena} achieving a acceptable accuracy for the generation of Datasets
\\

@@

  \bibitem{Hong:Lei}
~Hong. Y. Jeon, ~Lei F. Tian  and ~Heping Zhu, \emph{Robust Crop and Weed Segmentation under Uncontrolled Outdoor Ilumination} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2011.

@@
